---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Covariance Matrix Estimation via Macroeconomic Factor Modeling"
subtitle: "19776209"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Tiago Baltazar (19776209)"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, Western Cape, South Africa" # First Author's Affiliation
Email1: "tiagobaltazar15\\@gmail.com" # First Author's Email address

#Author2: "John Smith"
#Ref2: "Some other Institution, Cape Town, South Africa"
#Email2: "John\\@gmail.com"
#CommonAffiliation_12: FALSE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

#Author3: "John Doe"
#Email3: "Joe\\@gmail.com"

CorrespAuthor_1: FALSE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Asset Allocation \\sep Risk Parity \\sep Mean Variance Optimisation \\sep Volatility" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $19776209$
#BottomCFooter:
TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
#addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: ""   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This report compares the performance of two asset allocation strategies namely; Risk Parity and Mean Variance during periods of volatility in South Africa. Using South African financial data, the risk adjusted and information ratio of a unleverd Risk Parity Index porfolio and Tangency Index porfolio are compared. The research paper found that the Mean Variance Optimisation approach is an superior asset allocation strategy during periods of high volatility in South Africa.
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment=NA, fig.width = 5, fig.height = 3, fig.pos="H", fig.align = "l")

options(tinytex.verbose = TRUE)

# Loading Packages
library(pacman)
pacman::p_load(fmxdat, Texevier, knitr, kableExtra, tidyverse, dplyr, readr, covFactorModel,
               FinCovRegularization, xts, quantmod,
               lubridate, tbl2xts, corrplot, rmsfuns)

# Loading Data
## Factors
dat_Fac <- read.csv("./data/Factors_New.csv")

dat_Factors <- dat_Fac %>%
    pivot_longer(cols = starts_with("X"), names_to="date", values_drop_na = FALSE) %>%
    pivot_wider(names_from="Indicator.Name") %>%
    mutate_at("date", str_replace, "X", "") %>%
    arrange(date) %>% mutate(date=as.yearqtr(date, format = "%Y Q%q")) %>%
    mutate(Inflation=((CPI-lag(CPI))/lag(CPI))*100) %>% 
    select(-c("CPI", "GDP.Deflator")) %>%
    filter(date>"2004 Q4")

### Daily Factors

US_10Yr <- read_rds("./data/bonds_10y.rds")%>%
    filter(Name=="US_10Yr") %>%
    spread(Name, Bond_10Yr) 

comms <- read_rds("./data/comms.rds")
comms <- comms %>%
    filter(Name=="Bcom_Index") %>%
    spread(Name, Price)


VIX <- read_rds("./data/IV.rds")
VIX <- VIX %>%
    filter(Name=="VIX") %>%
    spread(Name, Price)

usdzar <- read_rds("./data/usdzar.rds")
usdzar$Name <- gsub("SouthAfrica_Cncy", "USDZAR", usdzar$Name)
usdzar <- usdzar %>% spread(Name, Price)

### Full (Daily) factors convert to Quarterly
dat_Factors_K <- left_join(US_10Yr, comms, by="date") %>%
  left_join(., VIX, by="date") %>%
  left_join(., usdzar, by="date") %>%   # First, combining the relevant datasets
  mutate(Date=as.yearqtr(date)) %>%     # Second, converting to quarterly
  group_by(Date) %>%                 
  filter(date==max(date)) %>%
  ungroup() %>%
  select(Date, US_10Yr, Bcom_Index, VIX, USDZAR) %>%
  rename(., date=Date) %>%
  filter(date>"2004 Q4") 

### Consolidated factors dataset
Factors <- left_join(dat_Factors_K, dat_Factors, by="date")  %>%
  mutate(across(.cols=-c("date", "US_10Yr", "MM.Rate", "Inflation"), .fns = ~log(.+1)-log(lag(.+1)) )) %>% #log differences taken for relevant variables
  mutate(across(.cols=c("US_10Yr", "MM.Rate", "Inflation"), .fns= ~log(.+1))) %>% # where differences not needed to be taken, variables were still converted to log terms
  filter(date<"2021 Q4" & date>"2004 Q4")


## Assets
new_dat_0 <- read_rds("./data/alsi.rds")

new_dat_0$Tickers <- gsub(" SJ Equity", "", new_dat_0$Tickers)
new_dat_0$Superindustryname[which(new_dat_0$Tickers == "MNP")] <- "Industrials"

### Tidying original data
new_dat <- new_dat_0 %>% 
  select(-c("Short.Name", "J203")) %>%
  mutate(Date=as.yearqtr(date)) %>%   # steps below construct the quarterly dataset to be used 
  group_by(Date) %>%                  # Macro factors only available at (minimum) quarterly frequency
  filter(date==max(date)) %>%
  ungroup() %>% 
  select(Date, Tickers, Return, Superindustryname) %>%
  rename(., date=Date) %>%
  filter(date<"2021 Q4")

T40 <- c("ABG", "AMS", "AGL", "ANG", "APN", "BHP", "BID",   # Creating vector of T40 constituents
         "BVT", "BTI", "CPI", "CLS", "CFR", "DSY", "EXX",
         "FSR", "GLN", "GFI", "GRT", "IMP", "INL", "INP",
         "MNP", "MRP", "MTN", "MCG", "NPN", "NED", "NRP",
         "NPH", "OMU", "PRX", "RNI", "SLM", "SOL", "SHP",
         "SSW", "SBK", "SPP", "VOD", "WHL")

### Final assets dataset
Assets <- new_dat %>% 
  filter(Tickers %in% T40) %>%
  select(-Superindustryname) %>%
  pivot_wider(names_from = Tickers, values_from = Return) 
  

### Separating Assets by industry

Assets_Industrial <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Industrials") %>%
    select(date, Tickers, Return) %>%
    pivot_wider(names_from = Tickers, values_from = Return)

Assets_Resources <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Resources") %>%
    select(date, Tickers, Return) %>% 
    pivot_wider(names_from = Tickers, values_from = Return) 

Assets_Financials <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Financials") %>%
    select(date, Tickers, Return) %>%
    pivot_wider(names_from = Tickers, values_from = Return) 

```



# Introduction \label{Intro}



As per @Flannery.. factor models are good shit!



# Literature Review \label{Lit}



# Exploratory Analysis \label{Explor}

As can be seen in Section \ref{Lit}

## Data and Descriptive Statistics

```{r Factors Description}

# Creating Table with Variable Descriptions

Fac_Names <- colnames(Factors[, -1])
Fac_Desc <- c("US Long-Term Bond Yields", "Bloomberg Commodities Index", "CBOE Volatility Index", "USD/ZAR Spot Price", "SA Money Market Rate", "SA Real Gross Domestic Product", "SA Real Gross Fixed Capital Formation", "Inflation (Consumer Prices)")
Fac_Source <- c("N. Katzke", "N. Katzke", "N. Katzke", "N. Katzke", "IMF International Financial Statistics", "IMF International Financial Statistics", "IMF International Financial Statistics", "IMF International Financial Statistics")

data.frame(Fac_Names, Fac_Desc, Fac_Source) %>% arrange(Fac_Names) %>% kable(caption="Macroeconomic Factors", align="l", col.names = c("Name", "Description", "Source"))%>%
  kable_styling(latex_options = "HOLD_position")

```


```{r Descriptive Stats}
# Creating Table with descriptive statistics for Macro Factors
data.frame(pastecs::stat.desc(Factors[, -1], basic=F)) %>% 
  dplyr::mutate_at(c("Real.GDP", "Real.INV"), funs(as.character(signif(., 3)))) %>%
  kable(caption="Summary Statistics: Macroeconomic Factors", digits=3, align="l", longtable=TRUE)%>%
  kable_styling(latex_options = "HOLD_position")

```

```{r T40 constituents}
# Creating Descriptive Table of T40 stocks and Industries

new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Financials") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Financials", align="l", col.names = c("Ticker", "Constituent"))%>%
  kable_styling(latex_options = "HOLD_position")

new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Industrials") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Industrials", align="l", col.names = c("Ticker", "Constituent"))%>%
  kable_styling(latex_options = "HOLD_position")

new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Resources") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Resources", align="l", col.names = c("Ticker", "Constituent"))%>%
  kable_styling(latex_options = "HOLD_position")
```


```{r Treatment of Missing Values, include=FALSE}

# Checking number of NA's for each asset

colSums(is.na(Assets[, -1])) %>% kable(caption="Assets Missing Values", align="l", col.names = "n") %>% kable_styling(latex_options = "HOLD_position") 


```

```{r Cleaning Data, include=FALSE}
# Cleaning data and creating log returns series
source("./code/missingreturns.R")

# Assets split by industry
## First select assets with less than 30% of observations missing. Then impute missing values using the above (sourced) function.
## Finally, take logs of the returns, use log(x+1) to account for periods with zero returns.

Financials_clean <- Assets_Financials %>% 
  select(where(~mean(is.na(.))< 0.7)) %>% 
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

Industrial_clean <- Assets_Industrial %>% 
  select(where(~mean(is.na(.))< 0.7)) %>% 
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

Resources_clean <- Assets_Resources %>% 
  select(where(~mean(is.na(.))< 0.7)) %>%
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

```

```{r Excluded Assets, include=FALSE}
# Checking which assets dropped out

T40[!T40%in%colnames(Assets[, -1] %>% select(where(~mean(is.na(.))< 0.7)))] %>% kable(caption="Assets Missing Variables", align="l", col.names = "n") %>% kable_styling(latex_options = "HOLD_position")

```

## Factor and Industry Plots

```{r, fig.cap="US Long-Term Bond Yields \\label{Fig1}"}
p.US <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, US_10Yr)) + labs(x="", y="", title="US 10Year") + theme_bw()

fmxdat::finplot(p.US, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="USDZAR Spot Price \\label{Fig2}"}
p.USDZAR <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, USDZAR)) + labs(x="", y="", title="USDZAR") + theme_bw()

fmxdat::finplot(p.USDZAR, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="CBOE VIX Volatility Index \\label{Fig3}"}
p.VIX <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, VIX)) + labs(x="", y="", title="VIX Volatility") + theme_bw()

fmxdat::finplot(p.VIX, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="Bloomberg Commodity Price Index \\label{Fig4}"}
p.Bcom_Index <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Bcom_Index)) + labs(x="", y="", title="Commodity Price") + theme_bw()

fmxdat::finplot(p.Bcom_Index, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Money Market Rate \\label{Fig5}"}
p.MM.Rate <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, MM.Rate)) + labs(x="", y="", title="SA Money Market Rate") + theme_bw()

fmxdat::finplot(p.MM.Rate, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Real GDP \\label{Fig6}"}
p.Real.GDP <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Real.GDP)) + labs(x="", y="", title="SA Real GDP") + theme_bw()

fmxdat::finplot(p.Real.GDP, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Real Gross Fixed Capital Formation \\label{Fig7}"}
p.Real.Inv <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Real.INV)) + labs(x="", y="", title="SA Real Investment") + theme_bw()

fmxdat::finplot(p.Real.Inv, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Consumer Price Inflation \\label{Fig8}"}
p.CPI <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Inflation)) + labs(x="", y="", title="SA Inflation") + theme_bw()

fmxdat::finplot(p.CPI, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```


```{r, fig.cap="Asset Returns by Industry \\label{Fig9}"}
p.Indus <- new_dat %>%
    filter(Tickers %in% T40) %>%
    mutate(date=as.Date(date)) %>%
    ggplot() + geom_line(aes(date, Return), color="steelblue", size=1.2, alpha=0.8) + theme_bw() + fmxdat::fmx_cols() + facet_wrap(~Superindustryname) + labs(x="Year")

fmxdat::finplot(p.Indus, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

# Empirical Analysis

## Methodology

## Model Estimation (by Industry)

```{r xts transformation}
Factors_xts <- Factors %>% 
  tbl2xts::tbl_xts()

Financials_xts <- Financials_clean %>% tbl_xts()
Industrial_xts <- Industrial_clean %>% tbl_xts()
Resources_xts <- Resources_clean %>% tbl_xts()

```

```{r Factor Model: Financials}
FM_Fin <- covFactorModel::factorModel(Financials_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Fin <- FM_Fin$Sigma  # Covariance Matrix
FM_Res_Fin <- FM_Fin$residual

```

```{r, fig.cap="Factor Analysis: Financials \\label{Fig10}"}
par(mfrow = c(1, 2))
barplot(FM_Fin$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Fin$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```

```{r Factor Model: Industrial}
FM_Ind <- covFactorModel::factorModel(Industrial_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Ind <- FM_Ind$Sigma  # Covariance Matrix
FM_Res_Ind <- FM_Ind$residual
```

```{r, fig.cap="Factor Analysis: Industrial \\label{Fig11}"}
par(mfrow = c(1, 2))
barplot(FM_Ind$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Ind$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```

```{r Factor Model: Resources}
FM_Res <- covFactorModel::factorModel(Resources_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Res <- FM_Res$Sigma  # Covariance Matrix
FM_Res_Res <- FM_Res$residual
```

```{r, fig.cap="Factor Analysis: Resources \\label{Fig12}"}
par(mfrow = c(1, 2))
barplot(FM_Res$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Res$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```


## Discussion of Results

\ref{Fig12}

# Conclusion

\newpage

# References

<div id="refs"></div>

\newpage

# Appendices


^[This is an example of a footnote by the way. Something that should also not be overused.]

Equations should be written as such:

\begin{align}
\beta = \sum_{i = 1}^{\infty}\frac{\alpha^2}{\sigma_{t-1}^2} \label{eq1} \\
\int_{x = 1}^{\infty}x_{i} = 1 \notag
\end{align}

If you would like to see the equations as you type in Rmarkdown, use $ symbols instead (see this for yourself by adjusted the equation):

$$
\beta = \sum_{i = 1}^{\infty}\frac{\alpha^2}{\sigma_{t-1}^2} \\
\int_{x = 1}^{\infty}x_{i} = 1
$$

Note again the reference to equation \ref{eq1}. Writing nice math requires practice. Note I used a forward slashes to make a space in the equations.


```{r ShortTable, results = 'asis'}

library(xtable)
data <- mtcars[1:5,] %>% tibble::as_tibble()

table <- xtable(data, caption = "Short Table Example \\label{tab1}")
  print.xtable(table,
             # tabular.environment = "longtable",
             floating = TRUE,
             table.placement = 'H',
             # scalebox = 0.3,
             comment = FALSE,
             caption.placement = 'bottom'
             )

```

To reference calculations __in text__, _do this:_ From table \ref{tab1} we see the average value of mpg is `r mean(mtcars[1:5,]$mpg)`.

Including tables that span across pages, use the following (note that I add below the table: ``continue on the next page''). This is a neat way of splitting your table across a page.

Use the following default settings to build your own possibly long tables. Note that the following will fit on one page if it can, but cleanly spreads over multiple pages:

```{r LongTable, results = 'asis'}

library(xtable)

data = mtcars %>% tibble::as_tibble()
  addtorow          <- list()
  addtorow$pos      <- list()
  addtorow$pos[[1]] <- c(0)
  addtorow$command  <- c(paste("\\hline \n",
                               "\\endhead \n",
                               "\\hline \n",
                               "{\\footnotesize Continued on next page} \n",
                               "\\endfoot \n",
                               "\\endlastfoot \n",sep=""))
table <- xtable(data, caption = "Long Table Example")
  print.xtable(table,
             tabular.environment = "longtable",
             floating = FALSE, # Leave this as is.
             table.placement = 'H', # Leave this as is.
             booktabs = T, # Aesthetics
             include.rownames = FALSE,  # Typically you don't want this in a table.
             add.to.row = addtorow, # For adding the Continued on next page part...
             comment = FALSE,
             caption.placement = 'top',  # Where do you want the caption?
             size="\\fontsize{12pt}{13pt}\\selectfont"  # Size of text in table..
             )
# See https://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf for table inspiration
```

\hfill



```{r, results = 'asis'}


if(!require(huxtable)) install.packages(huxtable)
library(huxtable)
data(diamonds, package = 'ggplot2')
Title <- "Regression Output"
Label <- "Reg01"
lm1 <- lm(price ~ carat, diamonds)
lm2 <- lm(price ~ depth, diamonds)
lm3 <- lm(price ~ carat + depth, diamonds)
htab <-
huxreg(lm1, lm2, lm3,
                statistics = c(N = "nobs", R2 = "r.squared"),
                note = "%stars%.") %>%
  set_caption(Title) %>%
  set_label(Label)
# More settings:
font_size(htab) <- 12
# Let's change regression names: this is slightly hacky, but works. Comment out this section to see what the default looks like:
  Names <- c( "Reg1", "Reg2", "Reg3")
  for(i in 1:length(Names)) {
    htab[1,][[1+i]] <- Names[i]
  }
# Now simply call the table:
htab

```





