---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Covariance Matrix Estimation via Macroeconomic Factor Modeling"
subtitle: "19776209"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Tiago Baltazar (19776209)"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, Western Cape, South Africa" # First Author's Affiliation
Email1: "tiagobaltazar15\\@gmail.com" # First Author's Email address

#Author2: "John Smith"
#Ref2: "Some other Institution, Cape Town, South Africa"
#Email2: "John\\@gmail.com"
#CommonAffiliation_12: FALSE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

#Author3: "John Doe"
#Email3: "Joe\\@gmail.com"

CorrespAuthor_1: FALSE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Factor Modeling \\sep Macroeconomic Factors \\sep Asset Returns \\sep Covariance Matrix" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $19776209$
#BottomCFooter:
TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
#addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: ""   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  This report aims to study the relationship between macroeconomic factors and South African asset returns. To this end, a macroeconomic factor model was fit for the top 40 assets listed on the JSE. By using a series of domestic, and global, macroeconomic factors, this study was able to determine the sensitivity of each of the assets to the macroeconomic factors. In addition to this, a covariance matrix of returns for the financial, industrial, and resource sectors was constructed using the macroeconomic factor model. 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment=NA, fig.width = 5, fig.height = 3, fig.pos="H", fig.align = "l")

options(tinytex.verbose = TRUE)

# Loading Packages
library(pacman)
pacman::p_load(fmxdat, Texevier, knitr, kableExtra, tidyverse, dplyr, readr, covFactorModel,
               FinCovRegularization, xts, quantmod,
               lubridate, tbl2xts, corrplot, rmsfuns)

# Loading Data
## Factors
dat_Fac <- read.csv("./data/Factors_New.csv")

dat_Factors <- dat_Fac %>%
    pivot_longer(cols = starts_with("X"), names_to="date", values_drop_na = FALSE) %>%
    pivot_wider(names_from="Indicator.Name") %>%
    mutate_at("date", str_replace, "X", "") %>%
    arrange(date) %>% mutate(date=as.yearqtr(date, format = "%Y Q%q")) %>%
    mutate(Inflation=((CPI-lag(CPI))/lag(CPI))*100) %>% 
    select(-c("CPI", "GDP.Deflator"))

### Daily Factors

US_10Yr <- read_rds("./data/bonds_10y.rds")%>%
    filter(Name=="US_10Yr") %>%
    spread(Name, Bond_10Yr) 

comms <- read_rds("./data/comms.rds")
comms <- comms %>%
    filter(Name=="Bcom_Index") %>%
    spread(Name, Price)


VIX <- read_rds("./data/IV.rds")
VIX <- VIX %>%
    filter(Name=="VIX") %>%
    spread(Name, Price)

usdzar <- read_rds("./data/usdzar.rds")
usdzar$Name <- gsub("SouthAfrica_Cncy", "USDZAR", usdzar$Name)
usdzar <- usdzar %>% spread(Name, Price)

### Full (Daily) factors convert to Quarterly
dat_Factors_K <- left_join(US_10Yr, comms, by="date") %>%
  left_join(., VIX, by="date") %>%
  left_join(., usdzar, by="date") %>%   # First, combining the relevant datasets
  mutate(Date=as.yearqtr(date)) %>%     # Second, converting to quarterly
  group_by(Date) %>%                 
  filter(date==max(date)) %>%
  ungroup() %>%
  select(Date, US_10Yr, Bcom_Index, VIX, USDZAR) %>%
  rename(., date=Date)

### Consolidated factors dataset
Factors <- left_join(dat_Factors_K, dat_Factors, by="date")  %>%
  mutate(across(.cols=-c("date", "US_10Yr", "MM.Rate", "Inflation"), .fns = ~log(.+1)-log(lag(.+1)) )) %>% #log differences taken for relevant variables
  mutate(across(.cols=c("US_10Yr", "MM.Rate", "Inflation"), .fns= ~log(.+1))) %>% # where differences not needed to be taken, variables were still converted to log terms
  filter(date<"2021 Q4" & date>"2004 Q4")


## Assets
new_dat_0 <- read_rds("./data/alsi.rds")

new_dat_0$Tickers <- gsub(" SJ Equity", "", new_dat_0$Tickers)
new_dat_0$Superindustryname[which(new_dat_0$Tickers == "MNP")] <- "Industrials"

### Tidying original data
new_dat <- new_dat_0 %>% 
  select(-c("Short.Name", "J203")) %>%
  mutate(Date=as.yearqtr(date)) %>%   # steps below construct the quarterly dataset to be used 
  group_by(Date) %>%                  # Macro factors only available at (minimum) quarterly frequency
  filter(date==max(date)) %>%
  ungroup() %>% 
  select(Date, Tickers, Return, Superindustryname) %>%
  rename(., date=Date) %>%
  filter(date<"2021 Q4")

T40 <- c("ABG", "AMS", "AGL", "ANG", "APN", "BHP", "BID",   # Creating vector of T40 constituents
         "BVT", "BTI", "CPI", "CLS", "CFR", "DSY", "EXX",
         "FSR", "GLN", "GFI", "GRT", "IMP", "INL", "INP",
         "MNP", "MRP", "MTN", "MCG", "NPN", "NED", "NRP",
         "NPH", "OMU", "PRX", "RNI", "SLM", "SOL", "SHP",
         "SSW", "SBK", "SPP", "VOD", "WHL")

### Final assets dataset
Assets <- new_dat %>% 
  filter(Tickers %in% T40) %>%
  select(-Superindustryname) %>%
  pivot_wider(names_from = Tickers, values_from = Return) 
  

### Separating Assets by industry

Assets_Industrial <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Industrials") %>%
    select(date, Tickers, Return) %>%
    pivot_wider(names_from = Tickers, values_from = Return)

Assets_Resources <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Resources") %>%
    select(date, Tickers, Return) %>% 
    pivot_wider(names_from = Tickers, values_from = Return) 

Assets_Financials <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Financials") %>%
    select(date, Tickers, Return) %>%
    pivot_wider(names_from = Tickers, values_from = Return) 

```



# Introduction \label{Intro}


Overall investment risk is typically classified as being either systematic (market), affecting the broader market, or idiosyncratic risk, which is unique to individual assets. While the latter can, in effect, be diversified away, the former affects a large portion of assets. Factor models can be used to explain the common (systematic) variation in asset returns, with the remaining variance, not explained by the factors, being unique to each individual security. Macroeconomic factor models use observable economic time series to explain the common variation in asset returns, with the remaining, unexplained, variance being asset-specific. This paper presents a series of eight macroeconomic factors to be used in studying the relationship between macroeconomic variables and the top 40 assets on the JSE. Factor loadings, describing each assets sensitivity to the macroeconomic factors, are presented, along with the estimated covariance matrix of asset returns for each super-industry, namely, the financial, industrial, and resource sectors. The rest of the paper is outlined as follows: Section \ref{Lit} presents a brief literature review, Section \ref{Explor} consists of an exploratory analysis of the variables used in the study. Section \ref{Emp} presents the results from the empirical analysis, and Section \ref{Conc} concludes. 



# Literature Review \label{Lit}

The use of modern, multivariate, factor models can be seen as an extension of the seminal work of @Sharpe1964's Capital Asset Pricing Model (CAPM), which used a single factor- the market portfolio- to estimate asset returns. In most cases, however, there are potentially, infinitely, many factors which can influence asset returns. Modern factor models allow one to address the curse of dimensionality by assuming stock returns are driven by a, more, limited set of factors. Factor models thus decompose asset returns into two components: one driven by the common variation between stocks, due to the factors, and another idiosyncratic component, unique to each asset. Using a factor model can therefore be a useful way of reducing the number of possible parameters which can, possibly, drive asset returns; assuming that what is not explained by the, common, factors is idiosyncratic risk unique to each asset.

Factor models have gained in prominence since @Sharpe1964, and have been extended to include more than one factor. In particular, this class of models can generally be split into three types [@Connor]; macroeconomic, statistical, and fundamental factor models. Whilst statistical factor models use only the input (data) to determine the relevant factors for asset returns, macroeceonmic and fundamental factor models rely on the researcher to supplement the asset returns data with factors. One of the most prominent fundamental factor model was developed by @Fama1992, who use firm-specific variables including relevant firm financial ratios, firm-size, and market beta in order to explain the variation in asset returns. 

In using macroeconomic factor models to study the behavior of asset returns, @Chen1986 propose a set of candidate economic variables as factors to explain systematic asset risk. They found that industrial production, changes in risk premium, some measures of inflation, and changes in the yield curve were all significant in explaining expected asset returns. In a similar vein, @Kim1987 find that an economic factor model, generally, performs better than a multivariate CAPM. The factors that they found to be significant were split into three categories: general, economy-wide, variables, the second category focused on the monetary side of the economy and included the interest rate and money supply. And the final factor comprised of labor market variables.  

\newpage

# Exploratory Analysis \label{Explor}

This section aims to provide a, brief, exploration of the data, justifying the choice of macroeconomic variables used as factors, as well as the treatment of the relevant assets. 

## Data and Descriptive Statistics

```{r Factors Description}

# Creating Table with Variable Descriptions

Fac_Names <- colnames(Factors[, -1])
Fac_Desc <- c("US Long-Term Bond Yields", "Bloomberg Commodities Index", "CBOE Volatility Index", "USD/ZAR Spot Price", "SA Money Market Rate", "SA Real Gross Domestic Product", "SA Real Gross Fixed Capital Formation", "Inflation (Consumer Prices)")
Fac_Source <- c("N. Katzke", "N. Katzke", "N. Katzke", "N. Katzke", "IMF International Financial Statistics", "IMF International Financial Statistics", "IMF International Financial Statistics", "IMF International Financial Statistics")

data.frame(Fac_Names, Fac_Desc, Fac_Source) %>% arrange(Fac_Names) %>% kable(caption="Macroeconomic Factors", align="l", col.names = c("Name", "Description", "Source"))%>%
  kable_styling(latex_options = "HOLD_position")

```


```{r Descriptive Stats}
# Creating Table with descriptive statistics for Macro Factors
data.frame(pastecs::stat.desc(Factors[, -1], basic=F)) %>% 
  kable(caption="Summary Statistics: Macroeconomic Factors", digits=3, align="l", longtable=TRUE)%>%
  kable_styling(latex_options = "HOLD_position")

```

Tables 3.1 and 3.2, respectively, provide a description of the factors included along with their sources, and summary statistics for the factors. Macroeconomic factors for South Africa were chosen on the basis of their possible influence in driving asset returns in South Africa. US 10 Year bond yields were used to quantify the influence of US Monetary Policy decisions in driving global liquidity. This is based on the direct relationship between bond yields and interest rates, whereby lower interest rates depress bond yields and these thus become a less attractive investment option; potentially leading investors to seek higher returns in domestic and foreign asset markets. The Bloomberg commodities index was used to measure the influence that changing commodity prices may have on asset returns, given that the South African economy is still influenced to a large extent by fluctuating commodity prices. The CBOE VIX volatility index was included to account for the effect that changing risk perceptions may have on domestic asset returns. Similarly to changes in US long term bond yields, lower risk perceptions may lead to capital flowing more towards developing (periphery) and could thus influence South African asset returns. The USDZAR spot rate was also included as changes in the price of foreign exchange can influence asset returns through, for example, increasing the cost of financing outstanding debt, or increasing input costs. The money market rate was used to represent the domestic monetary policy stance, this can affect the cost of borrowing for businesses, as well as changing investor incentives when it comes to investing in asset markets; both of which can influence returns. Real gross fixed capital formation was used to account for the level of investment in the economy for any given quarter. Finally, inflation was measured using the quarterly growth in the Consumer Price Index (CPI).



```{r T40 constituents}
# Creating Descriptive Table of T40 stocks and Industries

new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Financials") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Financials", align="l", col.names = c("Ticker", "Constituent"))%>%
  kable_styling(latex_options = "HOLD_position")
```

For this analysis, only variables in the Top 40 stocks in the JSE with the highest market capitalization were included. This was done to account for the fact that larger companies will be more exposed to global macroeconomic factors, relative to those with smaller market caps. The variables chosen as part of this "T40" are based on the FTSE Russell classification, as of the end of 2021 Q3 (see @FTSE).

```{r}
new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Industrials") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Industrials", align="l", col.names = c("Ticker", "Constituent"))%>%
  kable_styling(latex_options = "HOLD_position")
```

```{r}
new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Resources") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Resources", align="l", col.names = c("Ticker", "Constituent"))%>%
  kable_styling(latex_options = "HOLD_position")
```

\newpage

 After subsetting the Top 40 stocks, these were stratified into their respective super-industries. The stocks included, as well as their relevant industries, can be found in Tables 3.3-3.5 above. In order to estimate the covariance matrix, there could be no missing values in the asset returns data. Firstly, only those securities which had more than 70% of observations were considered, this led to five assets dropping out: NRP, OMU, RNI, MCG, and PRX. The former three were in financials, while the latter two were classified as industrials. And secondly, returns were imputed according to their own probability distribution. After this, there were no more missing values in the asset returns data.

```{r Treatment of Missing Values, include=FALSE}

# Checking number of NA's for each asset

colSums(is.na(Assets[, -1])) %>% kable(caption="Assets Missing Values", align="l", col.names = "n") %>% kable_styling(latex_options = "HOLD_position") 


```

```{r Cleaning Data, include=FALSE}
# Cleaning data and creating log returns series
source("./code/missingreturns.R")

# Assets split by industry
## First select assets with less than 30% of observations missing. Then impute missing values using the above (sourced) function.
## Finally, take logs of the returns, use log(x+1) to account for periods with zero returns.

Financials_clean <- Assets_Financials %>% 
  select(where(~mean(is.na(.))< 0.7)) %>% 
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

Industrial_clean <- Assets_Industrial %>% 
  select(where(~mean(is.na(.))< 0.7)) %>% 
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

Resources_clean <- Assets_Resources %>% 
  select(where(~mean(is.na(.))< 0.7)) %>%
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

```

```{r Excluded Assets, include=FALSE}
# Checking which assets dropped out

T40[!T40%in%colnames(Assets[, -1] %>% select(where(~mean(is.na(.))< 0.7)))] %>% kable(caption="Assets Missing Variables", align="l", col.names = "n") %>% kable_styling(latex_options = "HOLD_position")

```

## Data Visualization

This section presents figures for the relevant macroeconomic factors, and the asset returns (disaggregated) by industry. All macro factors entered the model in log terms, and, in addition, non-stationary variables were taken as quarterly changes. 

```{r, fig.cap="US Long-Term Bond Yields \\label{Fig1}"}
p.US <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, US_10Yr)) + labs(x="", y="", title="US 10Year") + theme_bw()

fmxdat::finplot(p.US, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="USDZAR Spot Price \\label{Fig2}"}
p.USDZAR <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, USDZAR)) + labs(x="", y="", title="USDZAR") + theme_bw()

fmxdat::finplot(p.USDZAR, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="CBOE VIX Volatility Index \\label{Fig3}"}
p.VIX <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, VIX)) + labs(x="", y="", title="VIX Volatility") + theme_bw()

fmxdat::finplot(p.VIX, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="Bloomberg Commodity Price Index \\label{Fig4}"}
p.Bcom_Index <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Bcom_Index)) + labs(x="", y="", title="Commodity Price") + theme_bw()

fmxdat::finplot(p.Bcom_Index, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Money Market Rate \\label{Fig5}"}
p.MM.Rate <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, MM.Rate)) + labs(x="", y="", title="SA Money Market Rate") + theme_bw()

fmxdat::finplot(p.MM.Rate, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Real GDP \\label{Fig6}"}
p.Real.GDP <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Real.GDP)) + labs(x="", y="", title="SA Real GDP") + theme_bw()

fmxdat::finplot(p.Real.GDP, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Real Gross Fixed Capital Formation \\label{Fig7}"}
p.Real.Inv <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Real.INV)) + labs(x="", y="", title="SA Real Investment") + theme_bw()

fmxdat::finplot(p.Real.Inv, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Consumer Price Inflation \\label{Fig8}"}
p.CPI <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Inflation)) + labs(x="", y="", title="SA Inflation") + theme_bw()

fmxdat::finplot(p.CPI, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```


```{r, fig.cap="Asset Returns by Industry \\label{Fig9}", fig.height=4, fig.width=7}
p.Indus <- new_dat %>%
    filter(Tickers %in% T40) %>%
    mutate(date=as.Date(date)) %>%
    ggplot() + geom_line(aes(date, Return), color="steelblue", size=1.2, alpha=0.8) + theme_bw() + fmxdat::fmx_cols() + facet_wrap(~Superindustryname) + labs(x="Year")

fmxdat::finplot(p.Indus, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

\newpage

# Empirical Analysis \label{Emp}

The model used to estimate covariance matrix parameters comprises of 8 macroeconomic factors, and 35 assets, disaggregated into their respective super-industries. The macroeconomic factor model was then applied to the three different industries, as these factors may affect assets in different industries differently. These three industry classes comprise of 10, 14, and 11 observations for the financial, industrial, and resources sectors, respectively. This section presents the main contribution of this paper, and the rest of it is set up as follows. Section \ref{Meth} presents the methodology used when constructing the macroeconomic factor model, Section \ref{Est} presents the results from estimating the model, and finally, Section \ref{Disc} provides a discussion of the main results. 

## Methodology \label{Meth}

The equation of the model is given by: 

\begin{align}
R_{ji,t}=\alpha_{ji} + \beta_{ji1}F_{1t} + ... + \beta_{jik}F_{kt} +...+\beta_{jiK}F_{Kt} +\epsilon_{it}
\end{align}

With **$F$** representing the 8 factors included in estimation, $\beta_{ik}$ representing the sensitivity of asset $i$ to factor $k$, $(k=1,...,K)$, for industry $j=(F,I,R)$. Factor models rely on three main assumptions. Firstly, individual factor realizations have zero expected value: $\mathbb{E}(f_k)=0$. Secondly, asset-specific errors are uncorrelated with each of the factors: $cov(f_{kt}, \epsilon_{it})=0$ $\forall$ $k$, $i$, & $t$. And, finally, that error terms are serially uncorrelated: $cov(\epsilon_{it}, \epsilon{ds})=0$ $\forall$ $i\neq d$, and $t \neq s$. From this, one then essentially has that: 

\begin{align}
Var(r_{i}) = L\phi L' + \sigma
\end{align}

With the above implying that the variance of individual assets is given by the sum of both the systematic and idiosyncratic risk components.

## Model Estimation \label{Est}

This section presents the results from estimating the macroeconomic factor model, with Figures \ref{Fig10}-\ref{Fig12} displaying the estimated **$\alpha$'s** and **$\beta$'s** for each industry, where $\beta$ represents each assets sensitivity to the factors, and $\alpha$ the constant (excess) returns.

```{r xts transformation}
Factors_xts <- Factors %>% 
  tbl2xts::tbl_xts()

Financials_xts <- Financials_clean %>% tbl_xts()
Industrial_xts <- Industrial_clean %>% tbl_xts()
Resources_xts <- Resources_clean %>% tbl_xts()

```

```{r Factor Model: Financials}
FM_Fin <- covFactorModel::factorModel(Financials_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Fin <- FM_Fin$Sigma  # Covariance Matrix
FM_Res_Fin <- FM_Fin$residual

Sigma_Fin <- cov(Financials_xts)
```

```{r, fig.cap="Factor Analysis: Financials \\label{Fig10}", fig.height=4.5, fig.width=7}
par(mfrow = c(1, 2))
barplot(FM_Fin$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Fin$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```

```{r Factor Model: Industrial}
FM_Ind <- covFactorModel::factorModel(Industrial_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Ind <- FM_Ind$Sigma  # Covariance Matrix
FM_Res_Ind <- FM_Ind$residual
Sigma_Ind <- cov(Industrial_xts)

```

```{r, fig.cap="Factor Analysis: Industrial \\label{Fig11}", fig.height=4.5, fig.width=7}
par(mfrow = c(1, 2))
barplot(FM_Ind$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Ind$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```

```{r Factor Model: Resources}
FM_Res <- covFactorModel::factorModel(Resources_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Res <- FM_Res$Sigma  # Covariance Matrix
FM_Res_Res <- FM_Res$residual
Sigma_Res <- cov(Resources_xts)

```

```{r, fig.cap="Factor Analysis: Resources \\label{Fig12}", fig.height=4.5, fig.width=7}
par(mfrow = c(1, 2))
barplot(FM_Res$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Res$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```



## Discussion of Results \label{Disc}

Figure \ref{Fig10} displays the output from the factor analysis for stocks in the financial sector. From this, one can see that these assets tend to have a greater (positive) sensitivity to the macroeconomic factors, whilst Sanlam (SLM) appears to generate the greatest excess return. Similarly, Figure \ref{Fig11} displays these results for the industrial sector, and Figure \ref{Fig12} for resources. In addition to this, Tables 7.3, 7.6, and 7.9 in the appendix present that estimated covariance matrices for each of the assets in each industry. From these, one can see that there are many assets which exhibit zero covariance relative to the others, implying that after controlling for the common macroeconomic factors, the variance between many of the asset returns is null. 

# Conclusion \label{Conc}

This paper attempted to investigate the relationship between South African assets in different industries and a series of macroeconomic factors. To this end, 35 securities, from the financial, industrial, and resources sectors, were considered, along with eight macroeconomic factors. The sensitivities (loadings) of each asset to the macroeconomic factors were presented in Section \ref{Est}, as well as the covariance matrices for each industry. Whilst the aim of this study was to consider macroeconomic factors in estimating the covariance matrix, future investigations could use regression analysis to supplement the study. Such as @Flannery, who use a GARCH to model the impact of macroeconomic conditions on asset returns, or as in @Maio2015 who use dynamic factor analysis for identifying macroeconomic factors, and a VAR to decompose asset returns.

\newpage

# References

<div id="refs"></div>

\newpage

# Appendix: Supplementary Tables

## Financial

```{r Beta_F}
FM_Fin$beta %>% kable(caption="Factor Beta's: Financial", align="l", digits = 4) %>% kable_styling(latex_options = "HOLD_position")
```

```{r Alpha_F}
FM_Fin$alpha %>% kable(caption="Factor Alpha's: Financial", align="l", digits = 4, col.names = "Alpha") %>% kable_styling(latex_options = "HOLD_position")
```

```{r Covariance Matrix_F}
covmat_Fin %>% kable(caption="Covariance Matrix: Financial", align="l", digits = 4) %>% kable_styling(latex_options = "HOLD_position")
```

\newpage

## Industrial

```{r Beta_I}
FM_Ind$beta  %>% kable(caption="Factor Beta's: Industrial", align="l", digits = 4) %>% kable_styling(latex_options = "HOLD_position")
```

```{r Alpha_I}
FM_Ind$alpha %>% kable(caption="Factor Alpha's: Industrial", align="l", digits = 4, col.names = "Alpha") %>% kable_styling(latex_options = "HOLD_position")
```

```{r Covariance Matrix_I}
covmat_Ind %>% kable(caption="Covariance Matrix: Industrial", align="l", digits = 4) %>%  kable_styling(latex_options = "HOLD_position")
```

\newpage

## Resources

```{r, Beta_R}
FM_Res$beta %>% kable(caption="Factor Beta's: Resources", align="l", digits = 4) %>% kable_styling(latex_options = "HOLD_position")
```

```{r, Alpha_R}
FM_Res$alpha %>% kable(caption="Factor Alpha's: Resources", align="l", digits = 4, col.names = "Alpha") %>% kable_styling(latex_options = "HOLD_position")
```

```{r Covariance Matrix_R}
covmat_Res %>% kable(caption="Covariance Matrix: Resources", align="l", digits = 4) %>%  kable_styling(latex_options = "HOLD_position")
```





