---
title: Covariance Matrix Estimation via Macroeconomic Factor Modeling
output:
  md_document:
    variant: markdown_github
always_allow_html: yes
---

```{r setup, results=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "left", fig.height = 3, fig.pos = "H", fig.width = 5,
                      message=FALSE, warning=FALSE, comment = NA)
library(pacman)
pacman::p_load(fmxdat, Texevier, knitr, kableExtra, tidyverse, dplyr, readr, covFactorModel,
               FinCovRegularization, xts, quantmod,
               lubridate, tbl2xts, corrplot, rmsfuns)

rm(list = ls()) # Cleaning environment:
gc() # garbage collection 
```

# File Overview

This README is intended to guide the reader through the code used in completing the investigation on the use of factor modeling for estimating the asset returns covariance matrix. The final PDF document compiled can be found in this folder, titled "Factor Model". 

Certain sections included here, such as those discussing the process of uploading and tidying the data, as well as the treatment of missing values are excluded from the final PDF output, but are included here for illustration purposes. In addition, much of the output found in this document, and none of the code, are available in the final PDF. The first section presents the code used in uploading and tidying the data for both the macroeconomic factors and the asset returns. The second consists of the introduction, as in the final PDF document, this is followed by a brief exploratory analysis, and finally a presentation of the empirical analysis. The final section concludes the document. 



# Uploading and Tidying Data


```{r Loading Data and Tidying: Factor data}
dat_Fac <- read.csv("./data/Factors_New.csv")

dat_Factors <- dat_Fac %>%
    pivot_longer(cols = starts_with("X"), names_to="date", values_drop_na = FALSE) %>%
    pivot_wider(names_from="Indicator.Name") %>%
    mutate_at("date", str_replace, "X", "") %>%
    arrange(date) %>% mutate(date=as.yearqtr(date, format = "%Y Q%q")) %>%
    mutate(Inflation=((CPI-lag(CPI))/lag(CPI))*100) %>% 
    select(-c("CPI", "GDP.Deflator"))  # previously had experimented with calculating inflation using GDP deflator, decided CPI inflation was better choice.

### Daily Factors

US_10Yr <- read_rds("./data/bonds_10y.rds")%>%
    filter(Name=="US_10Yr") %>%
    spread(Name, Bond_10Yr) 

comms <- read_rds("./data/comms.rds")
comms <- comms %>%
    filter(Name=="Bcom_Index") %>%
    spread(Name, Price)


VIX <- read_rds("./data/IV.rds")
VIX <- VIX %>%
    filter(Name=="VIX") %>%
    spread(Name, Price)

usdzar <- read_rds("./data/usdzar.rds")
usdzar$Name <- gsub("SouthAfrica_Cncy", "USDZAR", usdzar$Name)
usdzar <- usdzar %>% spread(Name, Price)

### Full (Daily) factors convert to Quarterly
dat_Factors_K <- left_join(US_10Yr, comms, by="date") %>%
  left_join(., VIX, by="date") %>%
  left_join(., usdzar, by="date") %>%   # First, combining the relevant datasets
  mutate(Date=as.yearqtr(date)) %>%     # Second, converting to quarterly
  group_by(Date) %>%                 
  filter(date==max(date)) %>%
  ungroup() %>%
  select(Date, US_10Yr, Bcom_Index, VIX, USDZAR) %>%
  rename(., date=Date) 

### Consolidated factors dataset
Factors <- left_join(dat_Factors_K, dat_Factors, by="date")  %>%
  mutate(across(.cols=-c("date", "US_10Yr", "MM.Rate", "Inflation"), .fns = ~log(.+1)-log(lag(.+1)) )) %>% #log differences taken for relevant variables
  mutate(across(.cols=c("US_10Yr", "MM.Rate", "Inflation"), .fns= ~log(.+1))) %>% # where differences not needed to be taken, variables were still converted to log terms
  filter(date<"2021 Q4" & date>"2004 Q4")

```


```{r Using new ALSI Data}
new_dat_0 <- read_rds("./data/alsi.rds")

new_dat_0$Tickers <- gsub(" SJ Equity", "", new_dat_0$Tickers)  # to make life easier

# Ticker MNP classified as being in both Resources and Industrials.
new_dat_0 %>% filter(Tickers=="MNP") %>%
  select(Tickers, Superindustryname) %>%
  distinct(Tickers, Superindustryname) %>%
  kable() %>% kable_styling(latex_options = "HOLD_position")

# According to JSE website, MNP's superindustry is industrials .. need to change this.
new_dat_0$Superindustryname[which(new_dat_0$Tickers == "MNP")] <- "Industrials"
# Checking again (with above code) confirms that MNP is now only classified as "Industrials"


# Tidying original data
new_dat <- new_dat_0 %>% 
  select(-c("Short.Name", "J203")) %>%
  mutate(Date=as.yearqtr(date)) %>%   # steps below construct the quarterly dataset to be used 
  group_by(Date) %>%                  # Macro factors only available at (minimum) quarterly frequency
  filter(date==max(date)) %>%
  ungroup() %>% 
  select(Date, Tickers, Return, Superindustryname) %>%
  rename(., date=Date) %>%
  filter(date<"2021 Q4")


T40 <- c("ABG", "AMS", "AGL", "ANG", "APN", "BHP", "BID",   # Creating vector of T40 constituents
         "BVT", "BTI", "CPI", "CLS", "CFR", "DSY", "EXX",
         "FSR", "GLN", "GFI", "GRT", "IMP", "INL", "INP",
         "MNP", "MRP", "MTN", "MCG", "NPN", "NED", "NRP",
         "NPH", "OMU", "PRX", "RNI", "SLM", "SOL", "SHP",
         "SSW", "SBK", "SPP", "VOD", "WHL")

# Final assets dataset
Assets <- new_dat %>% 
  filter(Tickers %in% T40) %>%
  select(-Superindustryname) %>%
  pivot_wider(names_from = Tickers, values_from = Return) 
  
# Separating Assets by industry

Assets_Industrial <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Industrials") %>%
    select(date, Tickers, Return) %>%
    pivot_wider(names_from = Tickers, values_from = Return)

Assets_Resources <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Resources") %>%
    select(date, Tickers, Return) %>% 
    pivot_wider(names_from = Tickers, values_from = Return) 

Assets_Financials <- new_dat %>%
    filter(Tickers %in% T40) %>%
    filter(Superindustryname=="Financials") %>%
    select(date, Tickers, Return) %>%
    pivot_wider(names_from = Tickers, values_from = Return) 


# Uncomment below to confirm number of observations (67) for each asset, same as factors

#Assets_Financials %>% gather(Tickers, Return, -date) %>% count(., Tickers)

#Assets_Industrial %>% gather(Tickers, Return, -date) %>% count(., Tickers)

#Assets_Resources %>% gather(Tickers, Return, -date) %>% count(., Tickers)

# Uncomment code below to verify that there is no overlap between variables and superindustries.

#colnames(Assets_Financials[, -1]) %in% colnames(Assets_Industrial[, -1])
#colnames(Assets_Financials[, -1]) %in% colnames(Assets_Resources[, -1])
#colnames(Assets_Resources[, -1]) %in% colnames(Assets_Industrial[, -1])

```


# Project Intro: Covariance Matrix Estimation via Macro Factor Modeling

- using factor models to estimate covariance matrix parameters
- assume stock returns are driven by a limited set of factors
- curse of dimensionality, need to reduce the number of parameters. Can use factor model

Factor model decomposition for asset returns

\begin{align}
$R_{it}=\alpha_{i} + \beta_{i1}F_{1t} + ... + \beta_{ik}F_{kt} +...+\beta_{iK}F_{Kt} +\epsilon_{it}$
\end{align}

With $\beta_{ik}$ representing the sensitivity of asset $i$ to factor $k$, $(k=1,...,K)$.

- trying to explain asset returns in terms of asset exposure wrt underlying risk factors. 
- have n=40 stocks, and k=8 macroeconomic factors
- can use factor model to estimate the variance and covariance of stock returns
- impose that residuals of two assets are uncorrelated
- if factor model well specified; factor model explains common variation between stock returns, what is left is idiosyncratic component
- Macro factor models are a type of explicit factor model vs
- implicit factor model driven by statistical factors from data. Sometimes prefered as it allows data to 'speak', telling us what the relevant factors are
-> using a factor model useful way of reducing number of possible parameters. Assuming what is not explained by factor model is idiosyncratic risk, unique to each asset.


Using factor analysis to explain the variation in stock returns for the T40 index using macroeconomic variables.
- Factor models decompose asset returns into low dimension factors and idiosynchratic residual noise:
-- In macro factor models, factors are observable economic time series

For this project I use the T40 returns dataset for stock returns: only accounting for large cap stocks, which will be more affected by movements in macroeconomic variables. 
- Variables had many returns missing, discarded ones which had more than 60% of observations missing. 
- For the rest, a function was called to draw values from the variables own probability distribution

The Palomar covFactor package was used to estimate alpha and beta coefficients for the stock returns.

The macroeconomic factors used are still based on the data used for the practical, namely the:
- US and SA 10_Yr bond spreads
- VIX volatility index
- Bloomberg commodities index


Macroeconomic factor models use observable economic time series as the factors. 

Factor models decompose the asset returns into an exposure term to some factors and a residual idiosyncratic component. The resulting covariance matrix contains a low-rank term corresponding to the factors and another full-rank term corresponding to the residual component.


These factors can include inflation, economic growth, interest rates, or exchange rates, among others. Macroeconomic factor models assume that the random return of each security responds linearly to the macroeconomic shocks.
use observable economic
time series as measures of the pervasive factors in
security returns

 As in all
factor models, each security also has an asset specific return unrelated to the factors security's linear sensitivities to the factors are called the factor betas of the security.

In a macroeconomic factor model, the factors
are defined by economic theory and observed
externally to the security returns data

# Exploratory Analysis

## Data and Descriptive Statistics

```{r Factors Description}
# Creating Table with Variable Descriptions
Fac_Names <- colnames(Factors[, -1])
Fac_Desc <- c("US 10 Year Bond Yields", "Bloomberg Commodities Index", "CBOE Volatility Index", "USD/ZAR Spot Price", "SA Money Market Rate", "SA Real Gross Domestic Product", "SA Real Gross Fixed Capital Formation", "Inflation (Consumer Prices)")
Fac_Source <- c("N. Katzke", "N. Katzke", "N. Katzke", "N. Katzke", "IMF International Financial Statistics", "IMF International Financial Statistics", "IMF International Financial Statistics", "IMF International Financial Statistics")

data.frame(Fac_Names, Fac_Desc, Fac_Source) %>% arrange(Fac_Names) %>% kable(caption="Macroeconomic Factors", align="l", col.names = c("Name", "Description", "Source")) #%>%  kable_styling(latex_options = "HOLD_position")

```

Macroeconomic factors for South Africa were chosen on the basis of their possible influence in driving asset returns in South Africa. US 10 Year bond yields were used to quantify the influence of US Monetary Policy decisions in driving global liquidity. This is based on the direct relationship between bond yields and interest rates, whereby lower interest rates depress bond yields and these thus become a less attractive investment option; potentially leading investors to seek higher returns in domestic and foreign asset markets. The Bloomberg commodities index was used to measure the influence that changing commodity prices may have on asset returns, given that the South African economy is still influenced to a large extent by fluctuating commodity prices. The CBOE VIX volatility index was included to account for the effect that changing risk perceptions may have on domestic asset returns. Similarly to changes in US long term bond yields, lower risk perceptions may lead to capital flowing more towards developing (periphery) and could thus influence South African asset returns. The USDZAR spot rate was also included as changes in the price of foreign exchange can influence asset returns through, for example, increasing the cost of financing outstanding debt, or increasing input costs. The money market rate was used to represent the domestic monetary policy stance, this can affect the cost of borrowing for businesses, as well as changing investor incentives when it comes to investing in asset markets; both of which can influence returns. Real gross fixed capital formation was used to account for the level of investment in the economy for any given quarter. Finally, inflation was measured using the Consumer Price Index (CPI) and the formula $Inflation_{t}=\frac{CPI_{t}-CPI_{t-1}}{CPI_{t-1}}$. All macro factors entered the model in log terms, and, in addition, non-stationary variables were taken as quarterly changes. 

Descriptive statistics for the macroeconomic factors can be seen in the table below.



```{r Descriptive Stats}
# Creating Table with descriptive statistics for Macro Factors
data.frame(pastecs::stat.desc(Factors[, -1], basic=F)) %>% 
  dplyr::mutate_at(c("Real.GDP", "Real.INV"), funs(as.character(signif(., 3)))) %>%
  kable(caption="Summary Statistics: Macro Factors", digits=3, align="l", longtable=TRUE) #%>%  kable_styling(latex_options = "HOLD_position")

```


For this analysis, only variables in the Top 40 of the JSE, by market capitalization, were included. This was done to account for the fact that larger companies will be more exposed to global macroeconomic factors, relative to those with smaller market caps. The variables chosen as part of this "T40" are based on the FTSE Russell classification, as of the end of 2021 Q4 (see [@FTSE]). After subsetting the Top 40 stocks, these were stratified into their respective super-industries. When constructing the dataset by industry classification, Mondi PLC (MNP) had the majority of it's observations classified as being in resources, rather than the industrial sector the JSE claims it belongs to. As such, MNP was reclassified as being part of Industrials. The stocks included, as well as their relevant industries, can be found in the table below. 

```{r T40 constituents}
# Creating Descriptive Table of T40 stocks and Industries
new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Financials") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Financials", align="l", col.names = c("Ticker", "Constituent")) #%>% kable_styling(latex_options = "HOLD_position")

new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Industrials") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Industrials", align="l", col.names = c("Ticker", "Constituent")) #%>% kable_styling(latex_options = "HOLD_position")

new_dat_0 %>% filter(Tickers %in% T40) %>%
  filter(Superindustryname=="Resources") %>%
  distinct(Tickers, Short.Name) %>%
  arrange(Short.Name) %>%
  kable(caption="T40 Constituents: Resources", align="l", col.names = c("Ticker", "Constituent")) #%>% kable_styling(latex_options = "HOLD_position")

```

### Treatment of Missing Values

The code below was run in order to check if there were missing values in the asset returns dataset, with column "n" representing the number of missing values. 

```{r Count Missing Values}
# Checking number of NA's for each asset
data.frame(colSums(is.na(Assets[, -1])))%>% kable(caption="Assets Missing Values", align="l", col.names = "n") #%>% kable_styling(latex_options = "HOLD_position") 

```


Removing the data was done as in the chunk below. Firstly, for each industry, assets which had more than 70% of observations missing were dropped. The reason for this is that the second step involves imputing the missing returns from the distribution of asset i's returns. Having a high proportion of missing observations would inevitably lead to biased results from using the "missingreturns" function.

```{r Clean Data}
# Cleaning data and creating log returns series
source("./code/missingreturns.R")

# Assets split by industry
## First select assets with less than 30% of observations missing. Then impute missing values using the above (sourced) function.
## Finally, take logs of the returns, use log(x+1) to account for periods with zero returns.

Financials_clean <- Assets_Financials %>% 
  select(where(~mean(is.na(.))< 0.7)) %>% 
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

Industrial_clean <- Assets_Industrial %>% 
  select(where(~mean(is.na(.))< 0.7)) %>% 
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

Resources_clean <- Assets_Resources %>% 
  select(where(~mean(is.na(.))< 0.7)) %>%
  impute_missing_returns(., impute_returns_method = "Drawn_Distribution_Own", Seed = as.numeric(format( Sys.time(), "%Y%d%H%M"))) %>%
  mutate(across(.cols=-date, .fns=~log(.+1))) 

```

From the table below, one can see the 5 tickers that dropped out of the final asset returns dataset. Tickers NRP, OMU, RNI, MCG, PRX dropping out, with the former 3 being part of the financials group, and the latter 2 belonging to industrials.

```{r Excluded Assets}
# Checking which assets dropped out

T40[!T40%in%colnames(Assets[, -1] %>% select(where(~mean(is.na(.))< 0.7)))] %>% kable(caption="Assets Missing Variables", align="l", col.names = "Tickers") #%>% kable_styling(latex_options = "HOLD_position")

```

## Data Visualization

This section presents figures for the relevant macroeconomic factors, and the asset returns (disaggregated) by industry. 

```{r, fig.cap="US Long-Term Bond Yields"}
p.US <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, US_10Yr)) + labs(x="", y="", title="US 10Year") + theme_bw()

fmxdat::finplot(p.US, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="USDZAR Spot Price"}
p.USDZAR <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, USDZAR)) + labs(x="", y="", title="USDZAR") + theme_bw()

fmxdat::finplot(p.USDZAR, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="CBOE VIX Volatility Index"}
p.VIX <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, VIX)) + labs(x="", y="", title="VIX Volatility") + theme_bw()

fmxdat::finplot(p.VIX, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="Bloomberg Commodity Price Index"}
p.Bcom_Index <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Bcom_Index)) + labs(x="", y="", title="Commodity Price") + theme_bw()

fmxdat::finplot(p.Bcom_Index, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Money Market Rate"}
p.MM.Rate <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, MM.Rate)) + labs(x="", y="", title="SA Money Market Rate") + theme_bw()

fmxdat::finplot(p.MM.Rate, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Real GDP"}
p.Real.GDP <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Real.GDP)) + labs(x="", y="", title="SA Real GDP") + theme_bw()

fmxdat::finplot(p.Real.GDP, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Real Gross Fixed Capital Formation"}
p.Real.Inv <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Real.INV)) + labs(x="", y="", title="SA Real Investment") + theme_bw()

fmxdat::finplot(p.Real.Inv, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```

```{r, fig.cap="South Africa Consumer Price Inflation"}
p.CPI <- Factors %>% mutate(date=as.Date(date)) %>% ggplot() + geom_line(aes(date, Inflation)) + labs(x="", y="", title="SA Inflation") + theme_bw()

fmxdat::finplot(p.CPI, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```


```{r, fig.cap="Asset Returns by Industry"}
p.Indus <- new_dat %>%
    filter(Tickers %in% T40) %>%
    mutate(date=as.Date(date)) %>%
    ggplot() + geom_line(aes(date, Return), color="steelblue", size=1.2, alpha=0.8) + theme_bw() + fmxdat::fmx_cols() + facet_wrap(~Superindustryname) + labs(x="Year")

fmxdat::finplot(p.Indus, x.vert = T, x.date.type = "%Y", x.date.dist="2 year", y.comma.sep=TRUE)

```


# Empirical Analysis

## Methodology

8 Macro Factors and 40 Assets

## Model Estimation



```{r xts transformation by industry}
Factors_xts <- Factors %>% 
  tbl2xts::tbl_xts()

Financials_xts <- Financials_clean %>% tbl_xts()
Industrial_xts <- Industrial_clean %>% tbl_xts()
Resources_xts <- Resources_clean %>% tbl_xts()


```

```{r Factor Model: Financials}
FM_Fin <- covFactorModel::factorModel(Financials_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Fin <- FM_Fin$Sigma  # Covariance Matrix
FM_Res_Fin <- FM_Fin$residual

```

```{r}
par(mfrow = c(1, 2))
barplot(FM_Fin$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Fin$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```

```{r Factor Model: Industrial}
FM_Ind <- covFactorModel::factorModel(Industrial_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Ind <- FM_Ind$Sigma  # Covariance Matrix
FM_Res_Ind <- FM_Ind$residual
```

```{r}
par(mfrow = c(1, 2))
barplot(FM_Ind$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Ind$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```

```{r Factor Model: Resources}
FM_Res <- covFactorModel::factorModel(Resources_xts, type="Macro", econ_fact = Factors_xts, rtn_Sigma = TRUE)

covmat_Res <- FM_Res$Sigma  # Covariance Matrix
FM_Res_Res <- FM_Res$residual
```

```{r}
par(mfrow = c(1, 2))
barplot(FM_Res$alpha, horiz = TRUE, 
        main = "alpha", col = "red", cex.names = 0.75, las = 1)
barplot(t(FM_Res$beta), horiz = TRUE, 
        main = "beta", col = "blue", cex.names = 0.75, las = 1)
```


# Conclusion

# References

# Appendices



































































